Analyzing tomographic images in Python with scikit-image

### 2016-08-17 skimage_tomo.tex
Caption of fig 3 + some work on first steps section

\title{scikit-image, a Python library for 2D and 3D image
processing}

@@

@@

@@

\begin{figure*}
    \centerline{\includegraphics[width=0.99\textwidth]{tomo_gallery}}
\caption{\csentence{Sample figure title.}
      A short description of the figure content
  should go here. \label{fig:tomo_gallery}}
\end{figure*}

>>>>

\title{Analyzing tomographic images in Python with scikit-image}

@@

\textcolor{blue}{text to be written to explain the following snippets of
code}

\begin{lstlisting}
>>> from skimage import filters
>>> im_gaussian = filters.gaussian(im)
\end{lstlisting}

\begin{lstlisting}
>>> im_gaussian = filters.gaussian(im, sigma=3, mode='wrap')
\end{lstlisting}

@@

\begin{lstlisting}
>>> from skimage import morphology
>>> labels = morphology.watershed(im, markers)
\end{lstlisting}

Most functions take indifferently 2-D or 3-D images as arguments, so that
the same functions can be used to process tomography and microscopy
images. Only a few functions do not support 3-D images and raise an error
when passed a 3-D argument:

\begin{lstlisting}
>>> filters.prewitt(im)
[...]
ValueError: The parameter `image` must be a 2-dimensional array
\end{lstlisting}

@@

\begin{figure*}
    \centerline{\includegraphics[width=0.99\textwidth]{tomo_gallery}}
    \caption{\csentence{Typical image processing operations with
	\texttt{scikit-image}.} From left to right and top to bottom.
	Data are syntheric, unless stated otherwise.
	\textbf{Filtering -} Top: non-local means denoising of an image
	with a fine-grained texture, acquired by \emph{in situ}
	synchrotron microtomography during
	glass melting~\citep{Gouillart2012}. Bottom: total-variation
	denoising of an image with two phases, corresponding to
	phase-separating silicate melts observed by \emph{in situ
	tomography}~\citep{Bouttes2015}.
	\textbf{Feature extraction -} Top: Hubble deep field (NASA,
	public domain), blob detection using the
	Laplacian of Gaussian method. Bottom: ??
	\textbf{Segmentation - } Top: super-pixel segmentation
	of a CT slice of the human head~\citep{tomo_wikipedia}, using
	Felzenszwalb's algorithm~\citep{Felzenszwalb2004}. Bottom: random
	walker segmentation (right) of noisy image (top-left corner), using
	histogram-determined markers (bottom-left corner).
	\textbf{Measures -} Top: visualization of local diameter
	(color-coded on the skeleton curve) of an
	interconnected phase (represented in violet).  Bottom: particles color-coded according
	to their extent.
\label{fig:tomo_gallery}}
\end{figure*}
